Open science and the future university researcher\thanks{This work is licensed under a \href{https://creativecommons.org/licenses/by/4.0/}{Creative Commons Attribution 4.0 International License} \ccby}

### 2017-02-07 paper-imagine-new-university.tex
more on challenges

Instead, cultural inertia and lack of institutional recognition\slash rewards pose
the most significant challenges to increased openness in science.

>>>>

Instead, cultural inertia and lack of institutional recognition\slash rewards pose
the most significant challenges to increased openness in science. In my opinion,
the biggest barrier is that most researchers either disagree on or are unaware of
the importance (and benefits) of working openly. Since they were not trained in
doing this, e.g., during graduate school or during postdoctoral training, they
also may simply be unaware of how to research openly, or the resources that are
available to do so. Furthermore, since most of their colleagues, collaborators,
and competitors do not practice open science, no pressure comes from the
research community to change.

This lack of pressure is related to the other major issue: lack of institutional
recognition and reward for open practices. In general, academic researchers will
do what gets them credit for promotion and tenure---anything beyond that requires
strong intrinsic motivation.
